\documentclass[conference,compsoc]{IEEEtran}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{cite}
\usepackage{graphicx}
\usepackage[caption=false,font=footnotesize]{subfig}
\usepackage{amsmath,amssymb,amsfonts,amsthm,mathtools,bm}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage[hidelinks]{hyperref}
\usepackage{microtype}

\interdisplaylinepenalty=2500

\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\newtheorem{remark}{Remark}

\DeclareMathOperator{\Law}{Law}
\DeclareMathOperator{\clip}{clip}
\DeclareMathOperator{\supp}{supp}
\DeclareMathOperator{\Ber}{Bernoulli}
\DeclareMathOperator{\Bin}{Binomial}
\DeclareMathOperator{\softmax}{softmax}
\DeclareMathOperator{\Diag}{Diag}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}

\newcommand{\R}{\mathbb{R}}
\newcommand{\N}{\mathcal{N}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\Prb}{\mathbb{P}}
\newcommand{\Ball}{\mathcal{B}}
\newcommand{\cZ}{\mathcal{Z}}
\newcommand{\cY}{\mathcal{Y}}
\newcommand{\cT}{\mathcal{T}}
\newcommand{\cH}{\mathcal{H}}
\newcommand{\TV}{\mathrm{TV}}
\newcommand{\dd}{\,\mathrm d}
\newcommand{\op}{\mathrm{op}}
\newcommand{\id}{\mathrm{id}}
\newcommand{\norm}[1]{\left\lVert #1\right\rVert}
\newcommand{\inner}[2]{\left\langle #1,#2\right\rangle}
\newcommand{\ind}[1]{\mathbf{1}\!\left\{#1\right\}}

\title{Ball-Local Reconstruction Bounds for Nonconvex DP-SGD Transcripts}

\author{
Joseph Margaryan
}

\begin{document}
\maketitle

\begin{abstract}
We study reconstruction of one training record from a nonconvex DP-SGD
transcript under a Ball-local prior on the hidden record.  The privacy and
reconstruction guarantees are indexed by a policy radius in a record metric,
so the relevant sensitivity is the change in the target contribution over a
metric ball rather than the worst-case clipped-gradient diameter.  The central
technical distinction is whether the adversary observes the Poisson inclusion
bits of the target record.  For the stronger known-inclusion transcript model,
we prove a Ball-local reconstruction-robustness bound by dominating the
adaptive transcript by a product of revealed Bernoulli--Gaussian experiments.
For homogeneous training schedules this product blow-up function is evaluated
exactly as a finite Binomial--Gaussian mixture.  The same revealed-inclusion
curve is a conservative certificate for hidden-inclusion adversaries, because
suppressing inclusion bits is post-processing.  We also record the hidden
Gaussian-mixture law pair, but treat its common scalar one-shift evaluator as a
special-case diagnostic rather than as the general Ball-substitution
certificate.  Finally, to align the transcript theory with concrete nonconvex
models, we prove explicit operator-2-norm tanh-gradient sensitivity bounds for
both binary and multiclass one-hidden-layer networks.
\end{abstract}

\section{Introduction}
\label{sec:introduction}

Differential privacy bounds reconstruction risk through a hypothesis-testing
statement about neighboring datasets.  In DP-SGD, however, the usual global
clipping sensitivity $2C$ can be much larger than the actual change in a
clipped per-example gradient when the hidden record is known to lie in a local
metric ball.  This paper develops the transcript-level analogue of Ball-local
Gaussian release bounds: the adjacency relation is local in the record metric,
and the reconstruction certificate depends on the Ball sensitivity
\[
\Delta_t(r)
:=
\sup_{d(z,u)\le r}
\norm{\bar g_t(z)-\bar g_t(u)}_2
\]
at each step rather than only on the clipping diameter.

The setting is deliberately separated into observation models.  If the
adversary observes the target inclusion indicators, the transcript is more
informative than the usual hidden-subsampling view.  We therefore certify the
known-inclusion model by a revealed Bernoulli--Gaussian product experiment.  If
the inclusion indicators are hidden, the hidden transcript is a post-processing
of the revealed transcript; hence the revealed curve is a valid conservative
certificate for hidden-inclusion adversaries as well.  One can additionally
study hidden-mixture f-DP curves, but the general Ball-substitution hidden law
is mixture-versus-mixture and is not, without extra assumptions, the familiar
one-shift subsampled Gaussian mixture.

The final ingredient is a model-level route to non-vacuous Ball sensitivities.
For projected tanh networks, if the hidden-layer weight matrix is controlled in
operator 2 norm and the output layer is controlled in operator 2 norm, the
record-gradient map is Lipschitz in the input with an explicit constant.  For
same-label substitutions in a label-preserving metric, this gives
\[
\Delta_t(r)\le \min\{L_z r,2C_t\},
\]
which is the quantity used in the transcript bounds.

\paragraph{Contributions}
The paper makes four contributions.
\begin{itemize}[leftmargin=1.5em]
    \item We formulate Ball-local reconstruction robustness for adaptive
    DP-SGD transcripts and prove a generic reduction from transcript law
    domination to reconstruction bounds.
    \item For known target inclusion bits, we dominate the adaptive transcript
    by a product of revealed Bernoulli--Gaussian experiments and give an exact
    homogeneous evaluator via a Binomial--Gaussian privacy-loss mixture.
    \item For hidden target inclusion bits, we show that the revealed curve is
    a conservative certificate by post-processing, and we separate this
    certificate from optional hidden-mixture diagnostics.
    \item We prove explicit binary and multiclass tanh-network $L_z$ bounds
    under operator-2-norm constraints on the weight matrices.  These theorems
    supply the model-aligned Ball sensitivities used by the transcript theory.
\end{itemize}

\section{Ball-local setup}
\label{sec:setup}

Let records live in a measurable space $\cZ$ equipped with a possibly extended
metric
\[
d:\cZ\times\cZ\to[0,\infty].
\]
A common supervised-learning specialization writes records as $(x,y)$ with
$x\in\R^d$ and $y$ in a finite label set.  The label-preserving Euclidean metric
is
\begin{equation}
\label{eq:label-preserving-metric}
d\big((x,y),(x',y')\big)
=
\begin{cases}
\norm{x-x'}_2, & y=y',\\
\infty, & y\ne y'.
\end{cases}
\end{equation}
Finite-radius adjacency under~\eqref{eq:label-preserving-metric} protects
changes to the feature vector conditional on the label; it does not protect
label changes.

Fix a public dataset fragment $D^-\in\cZ^{n-1}$ and write
\[
D_z=D^-\cup\{z\},
\qquad
D_u=D^-\cup\{u\}.
\]
The hidden record $Z$ is drawn from a Ball-local prior $\pi_{u,r}$ supported on
\[
\Ball(u,r):=\{z\in\cZ:d(z,u)\le r\}.
\]
A transcript mechanism produces
\[
\tau=\cT_T(D)=(\tilde S_1,\ldots,\tilde S_T),
\]
where $\tilde S_t$ is the sanitized update released at step $t$.  A
reconstructor is a measurable map from transcripts and side information to
records,
\[
R:\mathsf T\times\cZ^{n-1}\to\cZ.
\]
For reconstruction loss $\rho$ and tolerance $\eta$, the success probability is
\begin{equation}
\label{eq:success-probability}
p_{\rm succ}(\eta)
=
\Pr_{Z\sim\pi_{u,r},\,\tau\sim\Law(\cT_T(D_Z))}
\left[\rho\bigl(Z,R(\tau,D^-)\bigr)\le\eta\right].
\end{equation}

\begin{definition}[Prior anti-concentration]
For a prior $\pi$ and reconstruction loss $\rho$, define
\[
\kappa_{\pi,\rho}(\eta)
:=
\sup_{z_0\in\cZ}
\Pr_{Z\sim\pi}\left[\rho(Z,z_0)\le\eta\right].
\]
For exact identification on a finite support with prior weights
$\pi_1,\ldots,\pi_m$, this is $\max_i\pi_i$.  For a uniform finite prior it is
$1/m$.
\end{definition}

\section{Hypothesis-testing notation}
\label{sec:hypothesis-testing}

\begin{definition}[Blow-up function / randomized testing value]
For probability laws $P,Q$ on a common measurable space, define
\[
B_\kappa(P\|Q)
:=
\sup_{\phi:\,0\le \phi\le1,\; \E_Q\phi\le \kappa}
\E_P\phi,
\qquad
\kappa\in[0,1],
\]
where the supremum is over measurable randomized tests
$\phi:\mathsf X\to[0,1]$.  Equivalently, if $T_{Q,P}$ is the tradeoff function
with type-I error measured under $Q$ and power measured under $P$, then
\[
B_\kappa(P\|Q)=1-T_{Q,P}(\kappa).
\]
\end{definition}

The randomized-test formulation is important when the privacy-loss distribution
has atoms: the Neyman--Pearson optimum may randomize on a likelihood-ratio
level set.  It also makes $\kappa\mapsto B_\kappa(P\|Q)$ nondecreasing and
concave, because mixtures of feasible tests are feasible.  Throughout the
paper, $Q$ is the reference/null law and $P$ is the candidate/alternative law.
Thus any reconstruction event, or randomized reconstruction test, whose
reference probability is at most $\kappa$ has candidate probability at most
$B_\kappa(P\|Q)$.

\begin{lemma}[Post-processing]
\label{lem:post-processing}
If $K$ is a probability kernel, then
\[
B_\kappa(PK\|QK)\le B_\kappa(P\|Q),
\qquad
\kappa\in[0,1].
\]
\end{lemma}

\section{A local Ball-ReRo theorem}
\label{sec:local-rero}

For each $z\in\supp(\pi_{u,r})$, write
\[
P_z:=\Law(\cT_T(D_z)),
\qquad
Q_u:=\Law(\cT_T(D_u)).
\]

\begin{theorem}[Local Ball-ReRo]
\label{thm:local-ball-rero}
Let $\pi=\pi_{u,r}$.  Suppose there is a law pair $(P^\star,Q^\star)$ such that
for every $z\in\supp(\pi)$ and every $\kappa\in[0,1]$,
\[
B_\kappa(P_z\|Q_u)
\le
 g(\kappa)
:=
B_\kappa(P^\star\|Q^\star),
\]
where $g$ is nondecreasing and concave.  Then every measurable reconstructor
satisfies
\[
p_{\rm succ}(\eta)
\le
g\!\left(\kappa_{\pi,\rho}(\eta)\right).
\]
\end{theorem}

Theorem~\ref{thm:local-ball-rero} is the paper's basic reconstruction
reduction.  The remaining task is to find a dominating pair $(P^\star,Q^\star)$
for the transcript observation model of interest.

\section{Model-local gradient sensitivity}
\label{sec:model-local-sensitivity}

At step $t$, let $\theta_t$ be the current model parameter, possibly chosen
adaptively from the previous sanitized transcript.  Let
\[
g_t^h(z)=\nabla_\theta\ell(\theta_t^h;z)
\]
be the target per-example gradient at history $h$, and let
\[
\bar g_t^h(z):=\clip_{C_t}(g_t^h(z))
\]
be Euclidean clipping to the closed radius-$C_t$ ball.  Explicitly,
\[
\clip_C(v)=
\begin{cases}
v, & \norm{v}_2\le C,\\
C v/\norm{v}_2, & \norm{v}_2>C,
\end{cases}
\]
with $\clip_C(0)=0$.

\begin{assumption}[Gradient Lipschitzness in the record]
\label{assump:lz}
There is a parameter set $\Theta$ containing all iterates of interest and a
constant $L_z\ge0$ such that, for every $\theta\in\Theta$ and every same-label
pair under~\eqref{eq:label-preserving-metric},
\[
\norm{\nabla_\theta\ell(\theta;(x,y))
-
\nabla_\theta\ell(\theta;(x',y))}_2
\le
L_z\norm{x-x'}_2.
\]
Different-label pairs have infinite metric distance and impose no finite
constraint.
\end{assumption}

\begin{proposition}[From $L_z$ to stepwise Ball sensitivity]
\label{prop:lz-to-delta}
If Assumption~\ref{assump:lz} holds at step $t$, then
\[
\Delta_t(r)
:=
\sup_{h}\sup_{d(z,u)\le r}
\norm{\bar g_t^h(z)-\bar g_t^h(u)}_2
\le
\min\{L_z r,2C_t\}.
\]
\end{proposition}

The next two theorems provide explicit $L_z$ values for the binary and
multiclass tanh models used in the nonconvex transcript analysis.  The matrix
constraint is an operator-2-norm constraint,
\[
\norm{M}_{\op}:=\sup_{\norm{v}_2=1}\norm{Mv}_2.
\]
The parameter norm used for gradient clipping and transcript sensitivity is the
usual Euclidean/Frobenius product norm.

\begin{theorem}[Binary tanh MLP: operator-2-norm $L_z$ bound]
\label{thm:binary-tanh-op-lz}
Fix $H\in\mathbb N$ and $A,S,B>0$.  Consider
\[
f_\theta(x)=\frac1{\sqrt H}a^\top \tanh(Wx+b),
\qquad
\theta=(W,b,a),
\]
where
\[
W\in\R^{H\times d},
\qquad
b\in\R^H,
\qquad
a\in\R^H.
\]
For $y\in\{-1,+1\}$, let
\[
\ell(\theta;(x,y))
=
\log\bigl(1+\exp(-y f_\theta(x))\bigr).
\]
Assume $\norm{x}_2\le B$ and
\[
\Theta_{A,S}^{\rm bin}
:=
\{(W,b,a):\norm{W}_{\op}\le S,\ \norm{a}_2\le A\}.
\]
Equip parameter space with
\[
\norm{(\Delta W,\Delta b,\Delta a)}_2^2
=
\norm{\Delta W}_F^2+\norm{\Delta b}_2^2+\norm{\Delta a}_2^2.
\]
Let
\[
K_{\tanh}:=\
\sup_{u\in\R}|\tanh''(u)|=\frac{4}{3\sqrt3},
\]
\[
L_{\rm J}
:=
\frac1{\sqrt H}
\sqrt{
S^2+A^2K_{\tanh}^2S^2+A^2(K_{\tanh}SB+1)^2
},
\]
\[
G_{\rm J}
:=
\sqrt{1+\frac{A^2(1+B^2)}{H}},
\]
and
\[
L_z^{\rm bin}
:=
L_{\rm J}+\frac{AS}{4\sqrt H}G_{\rm J}.
\]
Then, for every $\theta\in\Theta_{A,S}^{\rm bin}$ and every same-label pair
$(x,y),(x',y)$,
\[
\norm{\nabla_\theta\ell(\theta;(x,y))
-
\nabla_\theta\ell(\theta;(x',y))}_2
\le
L_z^{\rm bin}\norm{x-x'}_2.
\]
Consequently, under the label-preserving metric, Assumption~\ref{assump:lz}
holds for this model with $L_z=L_z^{\rm bin}$.
\end{theorem}

\begin{theorem}[Multiclass tanh MLP: operator-2-norm $L_z$ bound]
\label{thm:multiclass-tanh-op-lz}
Fix $H\in\mathbb N$, a number of classes $K\ge2$, and $A,S,B>0$.  Consider the
logit map
\[
F_\theta(x)=\frac1{\sqrt H}V\tanh(Wx+b)\in\R^K,
\qquad
\theta=(W,b,V),
\]
where
\[
W\in\R^{H\times d},
\qquad
b\in\R^H,
\qquad
V\in\R^{K\times H}.
\]
For $y\in\{1,\ldots,K\}$, let
\[
\ell(\theta;(x,y))
=
-F_{\theta,y}(x)+\log\!\left(\sum_{c=1}^K e^{F_{\theta,c}(x)}\right).
\]
Assume $\norm{x}_2\le B$ and
\[
\Theta_{A,S}^{\rm mc}
:=
\{(W,b,V):\norm{W}_{\op}\le S,\ \norm{V}_{\op}\le A\}.
\]
Equip parameter space with
\[
\norm{(\Delta W,\Delta b,\Delta V)}_2^2
=
\norm{\Delta W}_F^2+\norm{\Delta b}_2^2+\norm{\Delta V}_F^2.
\]
Using the same $K_{\tanh}$, $L_{\rm J}$, and $G_{\rm J}$ as in
Theorem~\ref{thm:binary-tanh-op-lz}, define
\[
L_z^{\rm mc}
:=
\sqrt2\,L_{\rm J}+\frac{AS}{2\sqrt H}G_{\rm J}.
\]
Then, for every $\theta\in\Theta_{A,S}^{\rm mc}$ and every same-label pair
$(x,y),(x',y)$,
\[
\norm{\nabla_\theta\ell(\theta;(x,y))
-
\nabla_\theta\ell(\theta;(x',y))}_2
\le
L_z^{\rm mc}\norm{x-x'}_2.
\]
Consequently, under the label-preserving metric, Assumption~\ref{assump:lz}
holds for this model with $L_z=L_z^{\rm mc}$.
\end{theorem}

\section{Ball-SGD transcript domination}
\label{sec:transcript-domination}

At step $t$, conditional on a past history $h$, write the sanitized update as
\begin{align*}
\tilde S_t(D_u)&=C_t^h+I_t\bar g_t^h(u)+\xi_t,\\
\tilde S_t(D_z)&=C_t^h+I_t\bar g_t^h(z)+\xi_t,
\end{align*}
where $C_t^h$ contains all non-target contributions and deterministic
normalizations, $I_t\sim\Ber(q_t)$ is the Poisson inclusion bit for the target
record, and $\xi_t\sim\N(0,\sigma_t^2I_p)$.  Define the clipped gradient gap
\[
\delta_t^h(z,u):=\bar g_t^h(z)-\bar g_t^h(u),
\]
and choose deterministic Ball sensitivities satisfying
\[
\Delta_t(r)
\ge
\sup_{z\in\supp(\pi_{u,r})}\sup_h
\norm{\delta_t^h(z,u)}_2.
\]
The normalized sensitivity is
\[
c_t:=\frac{\Delta_t(r)}{\sigma_t}.
\]
For projected tanh models satisfying Theorem~\ref{thm:binary-tanh-op-lz} or
Theorem~\ref{thm:multiclass-tanh-op-lz}, Proposition~\ref{prop:lz-to-delta}
gives the concrete choice
\[
\Delta_t(r)=\min\{L_z r,2C_t\}.
\]

\subsection{Known inclusion: revealed transcript bound}
\label{sec:known-inclusion}

The known-inclusion adversary observes the target inclusion bits, or an
equivalent residualized transcript from which the target-present steps are
known.  The one-step revealed reference pair is
\[
Q_t^{\rm rev}=\Law(I_t,G_t),
\qquad
P_t^{\rm rev}=\Law(I_t,I_tc_t+G_t),
\]
where $G_t\sim\N(0,1)$ and $I_t\sim\Ber(q_t)$ are independent.  Define
\[
Q_{1:T}^{\rm rev}:=\bigotimes_{t=1}^T Q_t^{\rm rev},
\qquad
P_{1:T}^{\rm rev}:=\bigotimes_{t=1}^T P_t^{\rm rev}.
\]

\begin{theorem}[Known-inclusion Ball-ReRo]
\label{thm:known-inclusion-rero}
For the revealed-inclusion transcript model,
\[
p_{\rm succ}(\eta)
\le
B_{\kappa_{\pi,\rho}(\eta)}
\!\left(P_{1:T}^{\rm rev}\middle\|Q_{1:T}^{\rm rev}\right).
\]
\end{theorem}

\begin{corollary}[Safe hidden-inclusion certificate]
\label{cor:hidden-safe-by-revealed}
Suppose the hidden-inclusion transcript is obtained from the corresponding
revealed-inclusion transcript by suppressing the target inclusion bits and then
applying any further measurable post-processing.  Then the same bound holds for
hidden-inclusion adversaries:
\[
p_{\rm succ}^{\rm hid}(\eta)
\le
B_{\kappa_{\pi,\rho}(\eta)}
\!\left(P_{1:T}^{\rm rev}\middle\|Q_{1:T}^{\rm rev}\right).
\]
Thus the revealed curve is conservative for the weaker hidden-inclusion
observation model.
\end{corollary}

\subsection{Exact homogeneous revealed evaluator}
\label{sec:homogeneous-evaluator}

When $q_t=q$ and $c_t=c$ for all $t$, the privacy loss
\[
L=\log\frac{\dd P_{1:T}^{\rm rev}}{\dd Q_{1:T}^{\rm rev}}
\]
has a finite Binomial--Gaussian mixture form.  Let
\[
K_T:=\sum_{t=1}^T I_t\sim\Bin(T,q).
\]
Conditional on $K_T=k$,
\[
L\mid K_T=k,Q
\sim
\N\!\left(-\frac12kc^2,kc^2\right),
\]
and
\[
L\mid K_T=k,P
\sim
\N\!\left(+\frac12kc^2,kc^2\right),
\]
with an atom at $L=0$ when $k=0$.  The Neyman--Pearson event is an upper level
set of $L$.  Therefore
\[
B_\kappa(P_{1:T}^{\rm rev}\|Q_{1:T}^{\rm rev})
=
P[L>\tau_\kappa]+\theta P[L=\tau_\kappa],
\]
where $\tau_\kappa$ and $\theta\in[0,1]$ are chosen so that
\[
Q[L>\tau_\kappa]+\theta Q[L=\tau_\kappa]=\kappa.
\]
This gives an exact finite-mixture evaluator for the known-inclusion curve.

\subsection{Unknown inclusion: hidden mixtures and safe certification}
\label{sec:hidden-inclusion}

If the transcript does not reveal target inclusion bits, the hidden transcript
contains less information than the revealed transcript.  Therefore
Corollary~\ref{cor:hidden-safe-by-revealed} gives the certified bound we use by
default.  This avoids a common pitfall: the hidden-subsampling law for an
add/remove target model is not the same as the hidden law for a Ball-local
substitution model.

To see the distinction, fix a step and a history after residualizing known
non-target contributions and normalizing by $\sigma_t$.  In a general
Ball-substitution comparison $D_z$ versus $D_u$, the hidden one-step laws are
mixture-versus-mixture:
\begin{align*}
Q_{t,u}^{\rm hid}
&=(1-q_t)\N(0,I_p)+q_t\N(\mu_{t,u},I_p),\\
P_{t,z}^{\rm hid}
&=(1-q_t)\N(0,I_p)+q_t\N(\mu_{t,z},I_p),
\end{align*}
where
\[
\mu_{t,u}=\frac{\bar g_t^h(u)}{\sigma_t},
\qquad
\mu_{t,z}=\frac{\bar g_t^h(z)}{\sigma_t},
\qquad
\norm{\mu_{t,z}-\mu_{t,u}}_2\le c_t.
\]
The scalar hidden pair
\[
Q_t^{\rm add}=\N(0,1),
\qquad
P_t^{\rm add}=(1-q_t)\N(0,1)+q_t\N(c_t,1)
\]
is therefore an add/remove or zero-center special case, not the general
Ball-substitution certificate.  In that special case, the one-step privacy loss
under $Q_t^{\rm add}$ is
\begin{align*}
\ell_t(x)
&=
\log\left((1-q_t)+q_t\exp(c_tx-c_t^2/2)\right),\\
&\hspace{25mm} x\sim\N(0,1).
\end{align*}
The product privacy loss is $\sum_t\ell_t(X_t)$, and its distribution can be
computed by Gauss--Hermite quadrature and convolution.  We treat this as a
deterministic diagnostic/evaluator for the stated special-case hidden law.  For
the general Ball-substitution transcript, the safe certificate is the revealed
curve from Corollary~\ref{cor:hidden-safe-by-revealed}, unless one explicitly
computes or upper-bounds the full mixture-versus-mixture law pair above.

\section{RDP-to-ReRo conversion}
\label{sec:rdp-conversion}

If a mechanism satisfies an RDP bound
\[
D_\alpha(P\|Q)\le\varepsilon_\alpha,
\qquad \alpha>1,
\]
then H\"older's inequality gives
\[
B_\kappa(P\|Q)
\le
\min\left\{1,
\exp\left(
\frac{\alpha-1}{\alpha}
\left[\log\kappa+\varepsilon_\alpha\right]
\right)\right\}.
\]
Optimizing over orders gives
\[
\Gamma_{\rm RDP}(\kappa)
=
\inf_{\alpha>1}
\min\left\{1,
\exp\left(
\frac{\alpha-1}{\alpha}
\left[\log\kappa+\varepsilon_\alpha\right]
\right)\right\}.
\]
This is a certified reconstruction bound for the law pair accounted for by the
RDP accountant.  It should not be interpreted as a bound on the stronger
revealed-inclusion transcript unless the accountant explicitly includes the
released inclusion bits.  Conversely, the revealed curve remains a conservative
bound for hidden-inclusion adversaries because hiding bits is post-processing.

\section{Finite-prior exact-identification attacks}
\label{sec:finite-prior-attacks}

Let $S=\{z_1,\ldots,z_m\}$ be a public candidate support with prior weights
$\pi_i$.  The exact-identification baseline is
\[
\kappa_{\rm id}=\max_i\pi_i,
\]
and for a uniform finite prior, $\kappa_{\rm id}=1/m$.

After residualizing the known non-target batch contribution, a known-inclusion
Gaussian transcript has observations
\[
r_t=g_t(z_i)+\xi_t
\]
on target-present steps.  The exact finite-prior Bayes score is
\[
S_i^{\rm known}
=
\log\pi_i
-
\frac12
\sum_{t\in\mathcal I}
\frac{\norm{r_t-g_t(z_i)}_2^2}{\sigma_t^2},
\]
with the least-squares limit when all $\sigma_t$ are equal and the prior is
uniform.

For an add/remove or zero-center hidden-inclusion likelihood in which the
residualized target contribution is either absent or equal to $g_t(z_i)$,
\[
r_t=
\begin{cases}
\xi_t, & I_t=0,\\
g_t(z_i)+\xi_t, & I_t=1,
\end{cases}
\]
so the exact score for that observation model is
\begin{align*}
S_i^{\rm unknown}
&=
\log\pi_i
+
\sum_t
\log\Bigg[
(1-q_t)\exp\left(-\tfrac{\norm{r_t}_2^2}{2\sigma_t^2}\right)\\
&\qquad\qquad+
q_t\exp\left(-\tfrac{\norm{r_t-g_t(z_i)}_2^2}{2\sigma_t^2}\right)
\Bigg],
\end{align*}
up to candidate-independent constants.  The Bayes-optimal exact-identification
attack returns
\[
\widehat i=\argmax_i S_i.
\]
The known-inclusion attack should be compared with the revealed f-DP curve.  A
hidden-inclusion attack should be compared with a hidden-mixture curve only when
that curve matches the stated observation model; otherwise the revealed curve is
the conservative certified comparator.

\section{Relationship to prior ReRo work}
\label{sec:related}

Balle, Cherubin, and Hayes formalized reconstruction with informed adversaries
and showed that model releases can leak training data in regimes where the
adversary knows all but one record~\cite{balle2022}.  Hayes, Mahloujifar, and
Balle express reconstruction risk through the blow-up function and estimate
DP-SGD reconstruction bounds by approximating the relevant likelihood-ratio
distribution~\cite{hayes2023}.  Kaissis, Hayes, Ziller, and Rueckert emphasize
the hypothesis-testing interpretation of reconstruction bounds and the need to
separate analytic mechanism curves from numerical approximations~\cite{kaissis2023}.
Their Poisson-subsampled Gaussian mechanism is an add/remove hidden-subsampling
law: one side is a base Gaussian and the other is a mixture of a base Gaussian
and a shifted Gaussian.  This is exactly the scalar hidden law recorded in
Section~\ref{sec:hidden-inclusion}, but it is not the general Ball-substitution
law when the reference record $u$ also contributes if sampled.  This paper
specializes the same hypothesis-testing perspective to Ball-local DP-SGD
transcripts, uses randomized tests throughout the f-DP workflow, and separates
certified revealed-inclusion bounds from special-case hidden-mixture diagnostics.

The metric-local privacy viewpoint is complementary to standard DP: it keeps
the usual privacy semantics but changes the adjacency graph to protect
single-record substitutions only inside a chosen metric radius.  In the present
nonconvex transcript setting, this radius enters through $L_zr$ and hence
through the normalized shifts $c_t=\Delta_t(r)/\sigma_t$.

\section{Conclusion}
\label{sec:conclusion}

Ball-local transcript certificates require two separate ingredients.  The first
is an observation-model-specific hypothesis-testing curve.  The revealed curve
certifies known inclusion and conservatively certifies hidden inclusion by
post-processing, while optional hidden-mixture curves must match their exact law
pair.  The second is a model-specific Ball sensitivity.  The operator-2-norm
tanh theorems in this paper provide explicit $L_z$ constants
for projected binary and multiclass networks, yielding
$\Delta_t(r)\le\min\{L_zr,2C_t\}$ at each step.  Together, these results give a
complete theory pipeline from local metric adjacency to transcript-level
reconstruction certificates for nonconvex DP-SGD.

\bibliographystyle{IEEEtran}
\begin{thebibliography}{9}

\bibitem{dwork2014}
C.~Dwork and A.~Roth,
\newblock \emph{The Algorithmic Foundations of Differential Privacy}.
\newblock Foundations and Trends in Theoretical Computer Science, 2014.

\bibitem{abadi2016}
M.~Abadi et al.,
``Deep Learning with Differential Privacy,''
in \emph{Proc. ACM CCS}, 2016.

\bibitem{mironov2017}
I.~Mironov,
``R\'enyi Differential Privacy,''
in \emph{Proc. IEEE CSF}, 2017.

\bibitem{dong2022}
J.~Dong, A.~Roth, and W.~Su,
``Gaussian Differential Privacy,''
\emph{Journal of the Royal Statistical Society: Series B}, 2022.

\bibitem{balle2022}
B.~Balle, G.~Cherubin, and J.~Hayes,
``Reconstructing Training Data with Informed Adversaries,''
in \emph{Proc. IEEE S\&P}, 2022.

\bibitem{hayes2023}
J.~Hayes, S.~Mahloujifar, and B.~Balle,
``Bounding Training Data Reconstruction in DP-SGD,''
in \emph{Advances in Neural Information Processing Systems}, 2023.

\bibitem{kaissis2023}
G.~Kaissis, J.~Hayes, A.~Ziller, and D.~Rueckert,
``Bounding Data Reconstruction Attacks with the Hypothesis Testing
Interpretation of Differential Privacy,''
arXiv:2307.03928, 2023.

\end{thebibliography}

\appendices

\section{Proofs for the hypothesis-testing reductions}
\label{app:hypothesis-testing-proofs}

\subsection{Proof of Lemma~\ref{lem:post-processing}}

\begin{proof}
Let the input space be $(\mathsf X,\mathcal X)$ and the output space be
$(\mathsf Y,\mathcal Y)$.  Let $\psi:\mathsf Y\to[0,1]$ be any randomized output
test satisfying
\[
\E_{QK}\psi\le \kappa.
\]
Define the pulled-back input test
\[
(K\psi)(x):=\int \psi(y)K(x,\dd y).
\]
Then $0\le K\psi\le1$ and
\[
\E_Q[K\psi]=\E_{QK}\psi\le\kappa.
\]
By the definition of $B_\kappa(P\|Q)$,
\[
\E_{PK}\psi=
\E_P[K\psi]
\le
B_\kappa(P\|Q).
\]
Taking the supremum over all randomized output tests $\psi$ feasible for
$B_\kappa(PK\|QK)$ gives
\[
B_\kappa(PK\|QK)\le B_\kappa(P\|Q).
\]
\end{proof}

\subsection{Proof of Theorem~\ref{thm:local-ball-rero}}

\begin{proof}
For each record $z$, define the success event
\[
E_z:=\{\tau:\rho(z,R(\tau,D^-))\le\eta\}.
\]
Let
\[
\kappa_z:=Q_u(E_z).
\]
By the definition of $B_\kappa$,
\[
P_z(E_z)\le B_{\kappa_z}(P_z\|Q_u).
\]
By the assumed domination,
\[
B_{\kappa_z}(P_z\|Q_u)
\le
 g(\kappa_z).
\]
Averaging over $Z\sim\pi$ yields
\[
p_{\rm succ}(\eta)
=
\int P_z(E_z)\,\pi(\dd z)
\le
\int g(\kappa_z)\,\pi(\dd z).
\]
Since $g$ is concave,
\[
\int g(\kappa_z)\,\pi(\dd z)
\le
 g\!\left(\int \kappa_z\,\pi(\dd z)\right).
\]
It remains to bound the average reference mass.  By Tonelli's theorem,
\begin{align*}
\int \kappa_z\,\pi(\dd z)
&=
\int Q_u(E_z)\,\pi(\dd z)\\
&=
\int
\Pr_{Z\sim\pi}\!\left[\rho\bigl(Z,R(\tau,D^-)\bigr)\le\eta\right]
Q_u(\dd\tau).
\end{align*}
For a fixed transcript $\tau$, the reconstruction $R(\tau,D^-)$ is a single
point in $\cZ$.  Therefore the inner probability is at most
\[
\sup_{z_0\in\cZ}
\Pr_{Z\sim\pi}\left[\rho(Z,z_0)\le\eta\right]
=
\kappa_{\pi,\rho}(\eta).
\]
Thus
\[
\int \kappa_z\,\pi(\dd z)\le\kappa_{\pi,\rho}(\eta).
\]
Using that $g$ is nondecreasing gives
\[
p_{\rm succ}(\eta)
\le
 g\!\left(\kappa_{\pi,\rho}(\eta)\right).
\]
\end{proof}

\section{Proof of the \texorpdfstring{$L_z$}{Lz}-to-sensitivity step}
\label{app:lz-to-delta-proof}

\begin{proof}[Proof of Proposition~\ref{prop:lz-to-delta}]
Fix a history $h$ and two records $z,u$ with $d(z,u)\le r$.  Since the distance
is finite under the label-preserving metric, the labels agree.  By
Assumption~\ref{assump:lz},
\[
\norm{g_t^h(z)-g_t^h(u)}_2
\le
L_z d(z,u)
\le
L_z r.
\]
Euclidean clipping is the metric projection onto the closed Euclidean ball
$\{v:\norm{v}_2\le C_t\}$.  Metric projections onto closed convex sets in a
Hilbert space are nonexpansive, hence
\begin{align*}
\norm{\bar g_t^h(z)-\bar g_t^h(u)}_2
&=
\norm{\clip_{C_t}(g_t^h(z))-\clip_{C_t}(g_t^h(u))}_2\\
&\le
\norm{g_t^h(z)-g_t^h(u)}_2
\le
L_zr.
\end{align*}
Also, both clipped gradients have norm at most $C_t$, so the triangle
inequality gives
\[
\norm{\bar g_t^h(z)-\bar g_t^h(u)}_2
\le
\norm{\bar g_t^h(z)}_2+
\norm{\bar g_t^h(u)}_2
\le
2C_t.
\]
Both inequalities hold for every admissible history and every pair with
$d(z,u)\le r$.  Taking the supremum gives
\[
\Delta_t(r)\le\min\{L_zr,2C_t\}.
\]
\end{proof}

\section{Operator-norm tanh preliminaries}
\label{app:tanh-preliminaries}

Throughout Appendices~\ref{app:binary-tanh-proof} and
\ref{app:multiclass-tanh-proof}, write
\[
u:=Wx+b,
\qquad
h:=\tanh(u),
\qquad
q:=\tanh'(u),
\]
and similarly define $u',h',q'$ for $x'$.  Let
\[
\delta:=\norm{x-x'}_2.
\]
The operator-norm constraint gives
\[
\norm{u-u'}_2
=
\norm{W(x-x')}_2
\le
\norm{W}_{\op}\norm{x-x'}_2
\le
S\delta.
\]
Because $\tanh$ is $1$-Lipschitz,
\begin{equation}
\label{eq:tanh-h-diff}
\norm{h-h'}_2\le S\delta.
\end{equation}
Next,
\[
\tanh''(t)=-2\tanh(t)(1-\tanh^2(t)).
\]
If $s=|\tanh(t)|\in[0,1)$, then
\[
|\tanh''(t)|=2s(1-s^2).
\]
The derivative of $2s(1-s^2)$ is $2-6s^2$, so the maximum over $s\in[0,1]$ is
attained at $s=1/\sqrt3$.  Therefore
\[
K_{\tanh}=
\sup_{t\in\R}|\tanh''(t)|
=
2\frac1{\sqrt3}\left(1-\frac13\right)
=
\frac4{3\sqrt3}.
\]
Thus $\tanh'$ is $K_{\tanh}$-Lipschitz, and
\begin{equation}
\label{eq:tanh-q-diff}
\norm{q-q'}_2
\le
K_{\tanh}\norm{u-u'}_2
\le
K_{\tanh}S\delta.
\end{equation}
Finally,
\[
\norm{h}_2\le\sqrt H,
\qquad
\norm{q}_\infty\le1,
\qquad
\norm{x}_2\le B.
\]

\section{Proof of Theorem~\ref{thm:binary-tanh-op-lz}}
\label{app:binary-tanh-proof}

\begin{proof}
Fix $\theta=(W,b,a)\in\Theta_{A,S}^{\rm bin}$ and a same-label pair
$(x,y),(x',y)$.  Define
\[
f(x)=\frac1{\sqrt H}a^\top h,
\qquad
f(x')=\frac1{\sqrt H}a^\top h'.
\]
By~\eqref{eq:tanh-h-diff},
\begin{equation}
\label{eq:binary-score-diff}
|f(x)-f(x')|
\le
\frac1{\sqrt H}\norm{a}_2\norm{h-h'}_2
\le
\frac{AS}{\sqrt H}\delta.
\end{equation}

Let
\[
\rho(s):=(1+e^{-s})^{-1},
\qquad
\beta(x,y):=\rho(-yf(x)).
\]
The derivative of $\rho$ satisfies $|\rho'(s)|\le1/4$.  Therefore, by
\eqref{eq:binary-score-diff},
\begin{equation}
\label{eq:binary-beta-diff}
|\beta(x,y)-\beta(x',y)|
\le
\frac14|f(x)-f(x')|
\le
\frac{AS}{4\sqrt H}\delta.
\end{equation}
The logistic-loss gradient is
\begin{equation}
\label{eq:binary-loss-gradient-factorization}
\nabla_\theta\ell(\theta;(x,y))
=
-y\,\beta(x,y)\,\nabla_\theta f(x).
\end{equation}

We now bound the size and input-Lipschitz constant of $\nabla_\theta f(x)$.
The score-gradient blocks are
\begin{align*}
\nabla_a f(x)&=\frac1{\sqrt H}h,\\
\nabla_b f(x)&=\frac1{\sqrt H}(a\odot q),\\
\nabla_W f(x)&=\frac1{\sqrt H}(a\odot q)x^\top.
\end{align*}
Hence
\begin{align*}
\norm{\nabla_\theta f(x)}_2^2
&=
\frac1H\left(
\norm{h}_2^2+
\norm{a\odot q}_2^2+
\norm{(a\odot q)x^\top}_F^2
\right)\\
&\le
\frac1H\left(H+A^2+A^2B^2\right)
=
1+\frac{A^2(1+B^2)}H.
\end{align*}
Thus
\begin{equation}
\label{eq:binary-GJ-bound}
\norm{\nabla_\theta f(x)}_2\le G_{\rm J}.
\end{equation}

For the $a$ block,
\[
\norm{\nabla_a f(x)-\nabla_a f(x')}_2
=
\frac1{\sqrt H}\norm{h-h'}_2
\le
\frac{S}{\sqrt H}\delta.
\]
For the $b$ block,
\begin{align*}
\norm{\nabla_b f(x)-\nabla_b f(x')}_2
&=
\frac1{\sqrt H}\norm{a\odot(q-q')}_2\\
&\le
\frac{AK_{\tanh}S}{\sqrt H}\delta.
\end{align*}
For the $W$ block, add and subtract $(a\odot q')x^\top$:
\begin{align*}
&\norm{\nabla_W f(x)-\nabla_W f(x')}_F\\
&\quad=
\frac1{\sqrt H}
\norm{(a\odot q)x^\top-(a\odot q')x'^\top}_F\\
&\quad\le
\frac1{\sqrt H}\left(
\norm{a\odot(q-q')}_2\norm{x}_2
+
\norm{a\odot q'}_2\norm{x-x'}_2
\right)\\
&\quad\le
\frac{A}{\sqrt H}\bigl(K_{\tanh}SB+1\bigr)\delta.
\end{align*}
Combining the three blocks in the product parameter norm gives
\begin{equation}
\label{eq:binary-J-lipschitz}
\norm{\nabla_\theta f(x)-\nabla_\theta f(x')}_2
\le
L_{\rm J}\delta.
\end{equation}

Using~\eqref{eq:binary-loss-gradient-factorization} at $x$ and $x'$ and adding
and subtracting $-y\beta(x',y)\nabla_\theta f(x)$,
\begin{align*}
&\norm{\nabla_\theta\ell(\theta;(x,y))
-
\nabla_\theta\ell(\theta;(x',y))}_2\\
&\quad\le
|\beta(x,y)-\beta(x',y)|\,\norm{\nabla_\theta f(x)}_2\\
&\qquad+
\beta(x',y)\,
\norm{\nabla_\theta f(x)-\nabla_\theta f(x')}_2.
\end{align*}
Since $0\le\beta(x',y)\le1$, substituting
\eqref{eq:binary-beta-diff}, \eqref{eq:binary-GJ-bound}, and
\eqref{eq:binary-J-lipschitz} yields
\[
\norm{\nabla_\theta\ell(\theta;(x,y))
-
\nabla_\theta\ell(\theta;(x',y))}_2
\le
\left(L_{\rm J}+\frac{AS}{4\sqrt H}G_{\rm J}\right)\delta.
\]
This is the claimed bound with $L_z^{\rm bin}=L_{\rm J}+(AS/(4\sqrt H))G_{\rm J}$.
\end{proof}

\section{Proof of Theorem~\ref{thm:multiclass-tanh-op-lz}}
\label{app:multiclass-tanh-proof}

\begin{proof}
Fix $\theta=(W,b,V)\in\Theta_{A,S}^{\rm mc}$ and a same-label pair
$(x,y),(x',y)$.  Let
\[
F(x)=\frac1{\sqrt H}Vh,
\qquad
F(x')=\frac1{\sqrt H}Vh'.
\]
From~\eqref{eq:tanh-h-diff},
\begin{equation}
\label{eq:mc-logit-diff}
\norm{F(x)-F(x')}_2
\le
\frac1{\sqrt H}\norm{V}_{\op}\norm{h-h'}_2
\le
\frac{AS}{\sqrt H}\delta.
\end{equation}

Let
\[
p(x):=\softmax(F(x)),
\qquad
\alpha(x,y):=p(x)-e_y,
\]
where $e_y$ is the $y$th standard basis vector in $\R^K$.  The multiclass
cross-entropy gradient factors as
\begin{equation}
\label{eq:mc-gradient-factorization}
\nabla_\theta\ell(\theta;(x,y))
=
J_F(x)^\ast\alpha(x,y),
\end{equation}
where $J_F(x)$ is the Jacobian of the logit map with respect to the parameters
and $J_F(x)^\ast$ is its adjoint under the Euclidean/Frobenius parameter norm.

First, bound $\norm{\alpha(x,y)}_2$.  Since $p(x)$ is a probability vector,
\begin{align*}
\norm{p(x)-e_y}_2^2
&=(1-p_y(x))^2+
\sum_{c\ne y}p_c(x)^2\\
&\le
(1-p_y(x))^2+
\left(\sum_{c\ne y}p_c(x)\right)^2\\
&=2(1-p_y(x))^2
\le2.
\end{align*}
Thus
\begin{equation}
\label{eq:alpha-norm-bound}
\norm{\alpha(x,y)}_2\le\sqrt2.
\end{equation}

Second, bound the Lipschitz constant of $\alpha$.  The softmax Jacobian at a
probability vector $p$ is
\[
J_{\softmax}=\Diag(p)-pp^\top.
\]
It is symmetric.  For row $i$,
\[
\sum_j |(J_{\softmax})_{ij}|
=p_i(1-p_i)+\sum_{j\ne i}p_ip_j
=2p_i(1-p_i)
\le\frac12.
\]
Therefore $\norm{J_{\softmax}}_2\le1/2$.  Applying the mean-value theorem to
$x\mapsto\softmax(x)$ gives
\[
\norm{p(x)-p(x')}_2
\le
\frac12\norm{F(x)-F(x')}_2.
\]
Using~\eqref{eq:mc-logit-diff},
\begin{equation}
\label{eq:alpha-lipschitz}
\norm{\alpha(x,y)-\alpha(x',y)}_2
\le
\frac{AS}{2\sqrt H}\delta.
\end{equation}

We next bound the operator norm of $J_F(x)^\ast$ and the input-Lipschitz
constant of $J_F(x)^\ast$.  Fix an arbitrary vector $v\in\R^K$ with
$\norm{v}_2=1$.  The scalar projection $v^\top F(x)$ has gradients
\[
\nabla_V(v^\top F(x))=\frac1{\sqrt H}vh^\top,
\]
\[
\nabla_b(v^\top F(x))=\frac1{\sqrt H}\bigl(V^\top v\odot q\bigr),
\]
\[
\nabla_W(v^\top F(x))=
\frac1{\sqrt H}\bigl(V^\top v\odot q\bigr)x^\top.
\]
Thus
\begin{align*}
\norm{J_F(x)^\ast v}_2^2
&=
\frac1H\Big(
\norm{vh^\top}_F^2
+
\norm{V^\top v\odot q}_2^2\\
&\hspace{15mm}+
\norm{(V^\top v\odot q)x^\top}_F^2
\Big)\\
&\le
\frac1H\left(H+A^2+A^2B^2\right)
=
G_{\rm J}^2.
\end{align*}
Taking the supremum over $\norm{v}_2=1$ gives
\begin{equation}
\label{eq:mc-J-operator-bound}
\norm{J_F(x)^\ast}_{\op}\le G_{\rm J}.
\end{equation}

For the input-Lipschitz bound on the adjoint Jacobian, again fix
$\norm{v}_2=1$.  The $V$ block satisfies
\[
\frac1{\sqrt H}\norm{v(h-h')^\top}_F
=
\frac1{\sqrt H}\norm{v}_2\norm{h-h'}_2
\le
\frac S{\sqrt H}\delta.
\]
The $b$ block satisfies
\[
\frac1{\sqrt H}\norm{V^\top v\odot(q-q')}_2
\le
\frac{AK_{\tanh}S}{\sqrt H}\delta.
\]
For the $W$ block,
\begin{align*}
&\frac1{\sqrt H}
\left\|
\begin{aligned}
&(V^\top v\odot q)x^\top\\
&\quad-(V^\top v\odot q')x'^\top
\end{aligned}
\right\|_F\\
&\quad\le
\frac1{\sqrt H}\norm{V^\top v\odot(q-q')}_2\norm{x}_2\\
&\qquad+
\frac1{\sqrt H}\norm{V^\top v\odot q'}_2\norm{x-x'}_2\\
&\quad\le
\frac{A}{\sqrt H}\bigl(K_{\tanh}SB+1\bigr)\delta.
\end{align*}
Combining the blocks gives, for every unit $v$,
\[
\norm{(J_F(x)^\ast-J_F(x')^\ast)v}_2
\le
L_{\rm J}\delta.
\]
Taking the supremum over unit $v$ gives
\begin{equation}
\label{eq:mc-J-lipschitz}
\norm{J_F(x)^\ast-J_F(x')^\ast}_{\op}
\le
L_{\rm J}\delta.
\end{equation}

Now subtract the loss gradients using~\eqref{eq:mc-gradient-factorization}:
\begin{align*}
&\nabla_\theta\ell(\theta;(x,y))
-
\nabla_\theta\ell(\theta;(x',y))\\
&\quad=
J_F(x)^\ast\alpha(x,y)-J_F(x')^\ast\alpha(x',y)\\
&\quad=
\bigl(J_F(x)^\ast-J_F(x')^\ast\bigr)\alpha(x,y)\\
&\qquad+
J_F(x')^\ast\bigl(\alpha(x,y)-\alpha(x',y)\bigr).
\end{align*}
Taking norms and applying
\eqref{eq:alpha-norm-bound}, \eqref{eq:alpha-lipschitz},
\eqref{eq:mc-J-operator-bound}, and~\eqref{eq:mc-J-lipschitz},
\begin{align*}
&\norm{\nabla_\theta\ell(\theta;(x,y))
-
\nabla_\theta\ell(\theta;(x',y))}_2\\
&\quad\le
\norm{J_F(x)^\ast-J_F(x')^\ast}_{\op}
\norm{\alpha(x,y)}_2\\
&\qquad+
\norm{J_F(x')^\ast}_{\op}
\norm{\alpha(x,y)-\alpha(x',y)}_2\\
&\quad\le
\sqrt2\,L_{\rm J}\delta
+G_{\rm J}\frac{AS}{2\sqrt H}\delta.
\end{align*}
This proves the stated bound with
\[
L_z^{\rm mc}=\sqrt2\,L_{\rm J}+\frac{AS}{2\sqrt H}G_{\rm J}.
\]
\end{proof}

\section{Proofs for transcript domination}
\label{app:transcript-proofs}

\subsection{Proof of Theorem~\ref{thm:known-inclusion-rero}}

\begin{proof}
Fix a candidate $z\in\supp(\pi_{u,r})$.  We prove that the actual revealed
transcript pair $(P_z,Q_u)$ is a post-processing of the product reference pair
$(P_{1:T}^{\rm rev},Q_{1:T}^{\rm rev})$.  The conclusion then follows from
Lemma~\ref{lem:post-processing} and Theorem~\ref{thm:local-ball-rero}.

At step $t$, condition on a past history $h$.  Under both datasets the target
inclusion bit has law $I_t\sim\Ber(q_t)$.  If $I_t=0$, the target record makes
no contribution and the two conditional laws are identical after adding the
common center $C_t^h$ and Gaussian noise $\xi_t$.  If $I_t=1$, the conditional
mean shift between $D_z$ and $D_u$ is
\[
\delta_t^h(z,u)=\bar g_t^h(z)-\bar g_t^h(u),
\]
with
\[
\norm{\delta_t^h(z,u)}_2\le \Delta_t(r)=c_t\sigma_t.
\]
If $\delta_t^h(z,u)\ne0$, let
\[
e_t^h:=\frac{\delta_t^h(z,u)}{\norm{\delta_t^h(z,u)}_2},
\qquad
\lambda_t^h:=\frac{\norm{\delta_t^h(z,u)}_2}{\sigma_t}\le c_t.
\]
If $\delta_t^h(z,u)=0$, choose any unit vector $e_t^h$ and set
$\lambda_t^h=0$.

The scalar reference experiment supplies $(I_t,Y_t)$, where under
$Q_t^{\rm rev}$,
\[
Y_t\mid I_t=i\sim\N(0,1),
\]
and under $P_t^{\rm rev}$,
\[
Y_t\mid I_t=i\sim\N(ic_t,1).
\]
From this worst-case scalar experiment, construct an actual scalar
\[
X_t:=
\begin{cases}
Y_t, & I_t=0,\\
\displaystyle \frac{\lambda_t^h}{c_t}Y_t+\sqrt{1-\left(\frac{\lambda_t^h}{c_t}\right)^2}\,Z_t,
& I_t=1,
\end{cases}
\]
where $Z_t\sim\N(0,1)$ is independent.  When $c_t=0$, define $X_t=Z_t$; then
also $\lambda_t^h=0$.  Under the reference law $Q_t^{\rm rev}$, $X_t$ is
standard normal regardless of $I_t$.  Under the candidate law $P_t^{\rm rev}$,
conditional on $I_t=1$, $X_t\sim\N(\lambda_t^h,1)$, and conditional on
$I_t=0$, $X_t\sim\N(0,1)$.

Now draw independent orthogonal Gaussian noise
$\zeta_t\sim\N(0,I_p-e_t^h(e_t^h)^\top)$ and output
\[
\tilde S_t=C_t^h+I_t\bar g_t^h(u)+\sigma_t\bigl(X_te_t^h+\zeta_t\bigr).
\]
Under the reference law, this is
\[
C_t^h+I_t\bar g_t^h(u)+\xi_t.
\]
Under the candidate law, when $I_t=1$ the additional mean in the
$e_t^h$ direction is
\[
\sigma_t\lambda_t^h e_t^h=\delta_t^h(z,u),
\]
so the output law is
\[
C_t^h+I_t\bar g_t^h(z)+\xi_t.
\]
Thus the actual one-step conditional transition is a Markov kernel applied to
the one-step worst-case revealed experiment.

Because $\theta_t^h$, $C_t^h$, and $\delta_t^h(z,u)$ are measurable functions of
the past transcript, these one-step kernels can be composed adaptively over
$t=1,\ldots,T$ by the Ionescu--Tulcea construction.  Hence there exists a
global kernel $K_z$ such that
\[
P_{1:T}^{\rm rev}K_z=P_z,
\qquad
Q_{1:T}^{\rm rev}K_z=Q_u.
\]
By Lemma~\ref{lem:post-processing}, for every $\kappa\in[0,1]$,
\[
B_\kappa(P_z\|Q_u)
\le
B_\kappa(P_{1:T}^{\rm rev}\|Q_{1:T}^{\rm rev}).
\]
The right-hand side is independent of $z$.  Theorem~\ref{thm:local-ball-rero}
therefore gives
\[
p_{\rm succ}(\eta)
\le
B_{\kappa_{\pi,\rho}(\eta)}(P_{1:T}^{\rm rev}\|Q_{1:T}^{\rm rev}).
\]
\end{proof}

\subsection{Proof of Corollary~\ref{cor:hidden-safe-by-revealed}}

\begin{proof}
By assumption, the hidden transcript is obtained from the revealed transcript by
a probability kernel $K$ that deletes the inclusion bits and performs any
additional allowed post-processing.  If $P_z^{\rm hid},Q_u^{\rm hid}$ denote the
hidden transcript laws for candidate $z$ and center $u$, then
\[
P_z^{\rm hid}=P_z^{\rm rev}K,
\qquad
Q_u^{\rm hid}=Q_u^{\rm rev}K.
\]
Lemma~\ref{lem:post-processing} gives
\[
B_\kappa(P_z^{\rm hid}\|Q_u^{\rm hid})
\le
B_\kappa(P_z^{\rm rev}\|Q_u^{\rm rev}).
\]
The proof of Theorem~\ref{thm:known-inclusion-rero} bounds the right-hand side
by
\[
B_\kappa(P_{1:T}^{\rm rev}\|Q_{1:T}^{\rm rev}),
\]
uniformly over $z\in\supp(\pi_{u,r})$.  Applying
Theorem~\ref{thm:local-ball-rero} to the hidden transcript laws gives the
claimed hidden-inclusion reconstruction bound.
\end{proof}

\subsection{Derivation of the homogeneous revealed evaluator}

\begin{proof}
For one revealed step with parameters $(q,c)$, the observation is $(I,X)$.  The
inclusion bit has the same law under $P$ and $Q$, so it contributes no
likelihood-ratio term.  If $I=0$, both laws have $X\sim\N(0,1)$, so the
one-step privacy loss is zero.  If $I=1$, then under $Q$, $X\sim\N(0,1)$, and
under $P$, $X\sim\N(c,1)$.  The density ratio is
\[
\frac{\varphi(x-c)}{\varphi(x)}
=
\exp\left(cx-\frac12c^2\right),
\]
where $\varphi$ is the standard normal density.  Thus
\[
\ell(I,X)=I\left(cX-\frac12c^2\right).
\]
Under $Q$ and conditional on $I=1$, $cX-c^2/2\sim\N(-c^2/2,c^2)$.  Under $P$
and conditional on $I=1$, $X\sim\N(c,1)$, so
$cX-c^2/2\sim\N(c^2/2,c^2)$.

For $T$ independent homogeneous steps, let $K_T=\sum_t I_t$.  Conditional on
$K_T=k$, the privacy loss is a sum of $k$ independent Gaussian terms.  Therefore
under $Q$,
\[
L\mid K_T=k\sim\N\left(-\frac12kc^2,kc^2\right),
\]
and under $P$,
\[
L\mid K_T=k\sim\N\left(+\frac12kc^2,kc^2\right).
\]
When $k=0$, both are point masses at zero.  Since the inclusion-bit law is the
same under $P$ and $Q$, $K_T\sim\Bin(T,q)$ under both laws.

The Neyman--Pearson lemma states that, among events with $Q$-probability at
most $\kappa$, an upper level set of the likelihood ratio maximizes
$P$-probability.  Since the likelihood ratio is $e^L$, the optimal event is an
upper level set of $L$, with possible randomization at the threshold when there
is an atom.  Thus
\[
B_\kappa(P_{1:T}^{\rm rev}\|Q_{1:T}^{\rm rev})
=
P[L>\tau_\kappa]+\theta P[L=\tau_\kappa],
\]
where $\theta\in[0,1]$ is chosen so that
\[
Q[L>\tau_\kappa]+\theta Q[L=\tau_\kappa]=\kappa.
\]
\end{proof}

\section{Proof of the RDP-to-ReRo conversion}
\label{app:rdp-proof}

\begin{proof}
Let $\Lambda=\dd P/\dd Q$ and let $\phi$ be any randomized test with
$0\le\phi\le1$ and $\E_Q\phi\le\kappa$.  H\"older's inequality with conjugate
exponents $\alpha$ and $\alpha/(\alpha-1)$ gives
\begin{align*}
\E_P\phi
&=\int \phi\Lambda\,\dd Q\\
&\le
\left(\int \Lambda^\alpha\,\dd Q\right)^{1/\alpha}
\left(\int \phi^{\alpha/(\alpha-1)}\,\dd Q\right)^{(\alpha-1)/\alpha}.
\end{align*}
Because $0\le\phi\le1$, we have
$\phi^{\alpha/(\alpha-1)}\le\phi$, and hence the second factor is at most
$\kappa^{(\alpha-1)/\alpha}$.  By the definition of R\'enyi divergence,
\[
\int \Lambda^\alpha\,\dd Q
=
\exp\bigl((\alpha-1)D_\alpha(P\|Q)\bigr)
\le
\exp\bigl((\alpha-1)\varepsilon_\alpha\bigr).
\]
Therefore
\begin{align*}
\E_P\phi
&\le
\exp\left(\frac{\alpha-1}{\alpha}\varepsilon_\alpha\right)
\kappa^{(\alpha-1)/\alpha}\\
&=
\exp\left(
\frac{\alpha-1}{\alpha}
[\log\kappa+\varepsilon_\alpha]
\right).
\end{align*}
Taking the supremum over all feasible randomized tests $\phi$ gives the stated
bound on $B_\kappa(P\|Q)$.  Since probabilities are at most one, the minimum
with one is valid.  Optimizing over $\alpha>1$ gives $\Gamma_{\rm RDP}$.
\end{proof}

\section{Finite-prior likelihood derivation}
\label{app:finite-prior-proof}

For the known-inclusion model, conditional on candidate $z_i$ and selected
steps $\mathcal I$, the residualized observations are independent Gaussians
\[
r_t\mid z_i\sim\N(g_t(z_i),\sigma_t^2I).
\]
Thus the log-likelihood is
\[
\sum_{t\in\mathcal I}
\left[-\frac{p}{2}\log(2\pi\sigma_t^2)
-
\frac{\norm{r_t-g_t(z_i)}_2^2}{2\sigma_t^2}
\right].
\]
Adding $\log\pi_i$ and dropping constants independent of $i$ yields
$S_i^{\rm known}$.

For the add/remove or zero-center hidden-inclusion model, conditional on
$z_i$, each residualized observation has mixture density
\[
(1-q_t)\varphi_{\sigma_t}(r_t)
+
q_t\varphi_{\sigma_t}(r_t-g_t(z_i)),
\]
where $\varphi_{\sigma_t}$ is the centered Gaussian density with covariance
$\sigma_t^2I$.  Taking logarithms, adding $\log\pi_i$, and dropping the common
Gaussian normalization constants gives $S_i^{\rm unknown}$.  Therefore
maximizing the displayed scores is the Bayes-optimal MAP rule for that stated
finite-prior observation model.  For a general Ball-substitution hidden model,
the same MAP principle applies, but the candidate likelihood must use the full
mixture-versus-mixture/sequential transcript law rather than the scalar
one-shift special case.

\section{Ethics considerations}
\label{app:ethics}

This paper studies privacy guarantees and reconstruction attacks for machine
learning systems trained on potentially sensitive data.  The attack likelihoods
and reconstruction bounds are intended as audit tools for mechanisms whose
operators are authorized to evaluate their own privacy risk.  The theory does
not require recovering raw human-subject data, and any empirical use of these
methods should be restricted to datasets for which the evaluator has permission
to run reconstruction audits.  The main defensive recommendation is to report
reconstruction certificates together with the exact observation model assumed by
the adversary, because revealed-inclusion and hidden-inclusion transcripts imply
different risks.

\end{document}
